Analysis of Physical Activity Survey(2022)

### 2023-05-04 docs/paper.tex
setup pages

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Analysis of Physical Activity Survey(2022)},
  pdfauthor={Jonathan Goodwin},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Analysis of Physical Activity Survey(2022)}
\author{Jonathan Goodwin}
\date{12 February 2023}

@@

We analyzed the sources of water for two subsets of the Jordan population, urban and rural residents. From Table \ref{tab:tab2} and Table \ref{tab:tab3}, we can see that both Colorado is the state with the lowest rate of obesity and that Mississipi is the highest.

@@

In section \ref{Data} we talk about the process of gathering and analyzing the dataset and the variables. Then in section \ref{Model} we build a linear model for the rate of obesity. Then in section \ref{Results} we discuss the implications of the dataset presented. Finally in section \ref{Discussion} we discuss implications for the United States citizens, as well as the weakness of the study and the further investigation that may be useful to the topic of recreational activity support and physical activity in the United States.

@@

Table \ref{tab:tab1} gives a small look at the dataset.

@@

Both Muscle Training and 150min of Aerobic Training had significant p-values in this model of 0.0236 and 0.0027 respectively. Below Figure \ref{fig:fig5} shows the relationship between 150min of Aerobics training and Muscle Training compared to the rate of Obesity. There was strong positive correlation to people with 300min of aerobic training, and those who did muscle training or 150min of aerobic training so including that interaction was not beneficial. Additionally those that do no aerobic training at all are strongly negatively correlated with those that do 150min or more. Soi including that interaction was not beneficial to the model.

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/fig5-1.pdf}
\caption{\label{fig:fig5}Obesity vs 150min of Aerobics}
\end{figure}

And below Figure \ref{fig:fig6} shows us the relationship between the rate of obesity and the proportion of a states residents participating in muscle training excercises.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/fig6-1.pdf}
\caption{\label{fig:fig6}Obesity vs Muscle Training}
\end{figure}

@@

From Figure \ref{fig:fig1} we see a chart comparing the proportion of respondents who were obese based on the different states in the country. We can see from the chart that all states lie between a rate of 20\% and 35\% obese. The chart below is for 2011.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/fig1-1.pdf}
\caption{\label{fig:fig1}Bar plot of Obesity by State}
\end{figure}

Below Table \ref{tab:tab2}, shows the states with the lowest proportions of obesity.

@@

\caption{\label{tab:tab2}Lowest Obesity Rates By State}
\centering
\begin{tabular}[t]{cc}
\toprule
Colorado & 20.1\\
Hawaii & 21.4\\
Massachusetts & 22.2\\
New Jersey & 23\\
California & 23.4\\
\addlinespace
District of Columbia & 23.8\\
\bottomrule
\end{tabular}
\end{table}

And here Table \ref{tab:tab3} gives the states with the highest obesity rates.

\caption{\label{tab:tab3}Highest Obesity Rates by State}
\centering
\begin{tabular}[t]{cc}
\toprule
Mississippi & 34.6\\
Louisiana & 32.9\\
West Virginia & 31.7\\
Alabama & 31.4\\
Oklahoma & 30.9\\
\addlinespace
Arkansas & 30.8\\
\bottomrule
\end{tabular}
\end{table}

From these tables and the chart above we see the lowest obesity rate in the United States is Colorado with 20.1\% and the highest is Mississippi with 34.6\%. For this analysis we want to see whether physical activity factors such as aerobic excercise. Below in \ref{fig:fig2} however we will briefly see how these obesity rates have changed by the end of the decade.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/fig2-1.pdf}
\caption{\label{fig:fig2}Bar plot of Obesity by State}
\end{figure}

We see from \ref{fig:fig2} that the overall rate of obesity has clearly increased, however the states with the highest and lowest rates remain largely the same as we can see from Table \ref{tab:tab4} and Table \ref{tab:tab5} below.

@@

Below we now look at the proportion of state residents participating in aerobic activities for 150min or more per week as well as the proportion of residents participating in muscle strength training for at least 2 hours per week. We see in Table \ref{tab:tab10} and Table \ref{tab:tab11} some familiar states from the Obesity rate Tables \ref{tab:tab4} and Table \ref{tab:tab5}. Namely Alabama which was one of the highest rates for Obesity in the country also has low rates of Aerobic activity.

@@

We now look at muscle training in Tables \ref{tab:tab12} and Table \ref{tab:tab13}. Here we see many of the low obesity rate states from earlier, like Colorado, Florida and the District of Columbia.

@@

According to (Jason A Bennie 1, n.d.) ``meeting both aerobic and muscle-strengthening exercise guidelines was associated with a lower obesity prevalence, and associations were more pronounced for higher obesity classes.'' We found similar section \ref{Results}. However we also noted in the model that muscle training and aerobic activities did not fully explain the obesity problems of the United States. Suggesting that while physical activity may be important it is not the entire explanation for the increasing rates of obesity. Research suggest Americans currently consume too many calories, saturated fats, trans fasts and added sugars.((US) 2010).

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Analysis of Physical Activity Survey(2022)},
  pdfauthor={Jonathan Goodwin},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Analysis of Physical Activity Survey(2022)}
\author{Jonathan Goodwin}
\date{2022 March 7}

@@

We analyzed the sources of water for two subsets of the Jordan
population, urban and rural residents. From Table @ref(tab:tab2) and
Table @ref(tab:tab3), we can see that both Colorado is the state with
the lowest rate of obesity and that Mississipi is the highest.

@@

In section @ref(Data) we talk about the process of gathering and
analyzing the dataset and the variables. Then in section @ref(Model) we
build a linear model for the rate of obesity. Then in section
@ref(Results) we discuss the implications of the dataset presented.
Finally in section @ref(Discussion) we discuss implications for the
United States citizens, as well as the weakness of the study and the
further investigation that may be useful to the topic of recreational
activity support and physical activity in the United States.

@@

Table @ref(tab:tab1) gives a small look at the dataset.

@@

Both Muscle Training and 150min of Aerobic Training had significant
p-values in this model of 0.0236 and 0.0027 respectively. Below Figure
@ref(fig:fig5) shows the relationship between 150min of Aerobics
training and Muscle Training compared to the rate of Obesity. There was
strong positive correlation to people with 300min of aerobic training,
and those who did muscle training or 150min of aerobic training so
including that interaction was not beneficial. Additionally those that
do no aerobic training at all are strongly negatively correlated with
those that do 150min or more. Soi including that interaction was not
beneficial to the model.

@@

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/fig5-1.pdf}
\caption{Obesity vs 150min of Aerobics}
\end{figure}

And below Figure @ref(fig:fig6) shows us the relationship between the
rate of obesity and the proportion of a states residents participating
in muscle training excercises.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/fig6-1.pdf}
\caption{Obesity vs Muscle Training}
\end{figure}

@@

From Figure @ref(fig:fig1) we see a chart comparing the proportion of
respondents who were obese based on the different states in the country.
We can see from the chart that all states lie between a rate of 20\% and
35\% obese. The chart below is for 2011.

\begin{verbatim}
## $y
## [1] "Percent of Population"
## 
## attr(,"class")
## [1] "labels"
\end{verbatim}

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/fig1-1.pdf}
\caption{Bar plot of Obesity by State}
\end{figure}

Below Table @ref(tab:tab2), shows the states with the lowest proportions
of obesity. And Table @ref(tab:tab3) gives the states with the highest
obesity rates.

\begin{wraptable}{l}{0pt}

\caption{\label{tab:tab2}Lowest Obesity Rates By State}
\centering
\begin{tabular}[t]{cc}
\toprule
Colorado & 20.1\\
Hawaii & 21.4\\
Massachusetts & 22.2\\
New Jersey & 23\\
California & 23.4\\
\addlinespace
District of Columbia & 23.8\\
\bottomrule
\end{tabular}
\end{wraptable}

@@

\caption{\label{tab:tab3}Highest Obesity Rates by State}
\begin{tabular}[t]{cc}
\toprule
Mississippi & 34.6\\
Louisiana & 32.9\\
West Virginia & 31.7\\
Alabama & 31.4\\
Oklahoma & 30.9\\
\addlinespace
Arkansas & 30.8\\
\bottomrule
\end{tabular}
\end{table}

From these tables and the chart above we see the lowest obesity rate in
the United States is Colorado with 20.1\% and the highest is Mississippi
with 34.6\%. For this analysis we want to see whether physical activity
factors such as aerobic excercise. Below in @ref(fig:fig2) however we
will briefly see how these obesity rates have changed by the end of the
decade.

\begin{figure}
\centering
\includegraphics{paper_files/figure-latex/fig2-1.pdf}
\caption{Bar plot of Obesity by State}
\end{figure}

We see from @ref(fig:fig2) that the overall rate of obesity has clearly
increased, however the states with the highest and lowest rates remain
largely the same as we can see from Table @ref(tab:tab4) and Table
@ref(tab:tab5) below.

@@

Below we now look at the proportion of state residents participating in
aerobic activities for 150min or more per week as well as the proportion
of residents participating in muscle strength training for at least 2
hours per week. We see in Table @ref(tab:tab10) and Table
@ref(tab:tab11) some familiar states from the Obesity rate Tables
@ref(tab:tab4) and Table @ref(tab:tab5). Namely Alabama which was one of
the highest rates for Obesity in the country also has low rates of
Aerobic activity.

@@

We now look at muscle training in Tables @ref(tab:tab12) and Table
@ref(tab:tab13). Here we see many of the low obesity rate states from
earlier, like Colorado, Florida and the District of Columbia.

@@

According to (Jason A Bennie 1, n.d.) ``meeting both aerobic and
muscle-strengthening exercise guidelines was associated with a lower
obesity prevalence, and associations were more pronounced for higher
obesity classes.'' We found similar section @ref(Results). However we
also noted in the model that muscle training and aerobic activities did
not fully explain the obesity problems of the United States. Suggesting
that while physical activity may be important it is not the entire
explanation for the increasing rates of obesity. Research suggest
Americans currently consume too many calories, saturated fats, trans
fasts and added sugars.((US) 2010).
